\vspace{-1cm} \bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}

### 2018-03-08 latex/paper.tex
Add package for better word spacing
Edits from B. Durand's review

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
\usepackage[charter]{mathdesign}
\usepackage[numbers]{natbib}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{lineno}
\usepackage{setspace}
\graphicspath{{../figures/}}
\bibliographystyle{unsrtcurrbiol}

@@

    Ciliogenesis begins with the assembly of a nascent TZ at the tips of
    the basal body \citep{reiter2012base}.
    This nascent TZ undergoes maturation, during which its structure and protein
    composition changes, allowing for the
    establishment of a compartmentalized ciliary space bounded by the ciliary membrane
    and the TZ in which axoneme assembly and signalling can occur.
    The axoneme is a microtubule-based structure that forms the core of all cilia and flagella.
    In the Drosophila male germline, nascent TZs first assemble on basal bodies
    during early G2 phase in spermatocytes \citep{riparbelli2012assembly}.
    This is followed by anchoring of cilia to the plasma membrane,
    rearrangment of microtubules within the TZ \citep{gottardo2013cilium},
    and establishment of a
    ciliary membrane that will persist through meiosis
    \citep{riparbelli2012assembly} (Figure 1A).
    TZ maturation has been described in
    \textit{Paramecium} \citep{aubusson2015transition}
    \textit{Caenorrhabditis elegans} \citep{serwas2017centrioles} and
    \textit{Drosophila melanogaster} \citep{gottardo2013cilium},
    and is most readily observed by an increase in TZ length
    in the Drosophila male germline.

@@

    %
    %   Results - 1
    %
    \subsection{\PIP{} is essential for transition zone maturation}
    To investigate how the reduction of cellular \PIP{} affects ciliogenesis in the
    Drosophila male germline,
    we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
    under the spermatocyte-specific $\beta$2-tubulin promoter (referred to herein as \sigd{}),
    \citep{wei2008depletion, fabian2010phosphatidylinositol}.
    SigD dephosphorylates \PIP{} \textit{in vivo},
    and we previously showed that \sigd{} induces male sterility
    due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
    To examine whether these were caused by aberrant TZ function,
    we examined the localization of fluorescently-tagged
    centriolar/basal body protein
    Ana1 (homolog of CEP295) \citep{goshima2007genes, blachon2009proximal}
    and the conserved TZ protein Cep290 \citep{basiri2014migrating}
    during early steps of cilium assembly in spermatocytes in both
    wild-type controls and \sigd{}.
    As shown in Figure 1,
    while Cep290 looks similar in control and \sigd{} in early G2 phase
    when TZs are still immature, 
    it grows to significantly longer lengths in \sigd{}
    compared to wild-type controls by the end of the G2 phase following
    the period of TZ maturation in spermatocytes.
    In contrast to the \textit{cep290} mutant, which contains
    longer than normal basal bodies \citep{basiri2014migrating},
    Ana1 length was not affected in \sigd{},
    and we did not observe a strong
    correlation between Cep290 and Ana1 lengths (Figure 1C).
    TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
    Mks1 \citep{vieillard2016transition}
    showed hyperelongation in \sigd{} (Figure 1D),
    suggesting that this phenotype is not specific to Cep290 but is shared
    by other members of the Drosophila TZ.
    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%
    in spermatocytes at late G2 phase)
    and showed high intra-cyst correlation (\textgreater 0.95) suggestive
    of a dosage-based response to a shared cellular factor,
    presumably SigD.
    Despite the persistence of hyperelongated TZs through meiosis,
    axonemes were able to
    elongate normally in post-meiotic cells (Figure 1E).
    However, as we showed previously, the ultrastructure of these axonemes
    was frequently aberrant,
    either lacking symmetry completely or containing triplet microtubules
    in addition to the usual doublets \citep{wei2008depletion}.

@@

   % Since Sktl expression suppressed TZ hyperelongation,
   % we investigated whether Sktl could localize to centrioles or cilia
   % in the Drosophila germline.
    Xu \textit{et al}. showed the vertebrate PIPKI$\gamma$ to be
    important for cilium formation in cultured cell lines
    \citep{xu2014pipkigamma}.
    As shown in Figure 2D, Drosophila PIPKIs arose from the recent duplication of
    the ancestral PIPKI gene,
    and are not orthologous to specific vertebrate PIPKI isoforms.
    Sktl has diverged more than its paralog PIP5K59B, and seems
    to be functionally related to PIPKI$\gamma$ in its roles at cilia,
    as well as the \textit{C. elegans} PPK-1 (See supplementary data in \citep{xu2014pipkigamma}).
    However, unlike the human PIPKI$\gamma$, which functions to license TZ assembly
    by promoting CP110 removal from basal bodies \citep{xu2016phosphatidylinositol},
    our results suggest that Sktl functions in
    regulating TZ length in the Drosophila male germline
    but not TZ assembly.
    Cp110 is dispensable for cilium formation in Drosophila \citep{franz2013cp110}
    and we found its localization to be unaffected in \sigd{} (Supplementary figure 1).

@@

    %
    %   Results - 4
    %
    \subsection{The \textit{onion rings} mutant decouples defects found in cells with reduced levels of \PIP{}}
    We previously showed that male flies homozygous for the \textit{onion rings}
    (\textit{onr}) mutant of Drosophila Exo84 were sterile, and had phenotypes
    similar to \sigd{} such as defects in cell polarity \citep{wei2008depletion}.
    Exo84 is a component of the octameric exocyst complex, which binds
    \PIP{} and regulates membrane trafficking at the plasma membrane.
    To investigate whether defects in TZ hyperelongation could be explained by
    defective Exo84 function, we examined TZs in \textit{onr} mutants.
    We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 5C),
    suggesting that Exo84 is dispensable for TZ maturation.

    Due to the involvement of exocyst in membrane trafficking at the plasma membrane,
    we examined whether cilium-associated membrane dynamics were affected in \sigd{}
    or \textit{onr} mutants similar to \textit{dila; cby} mutants
    \citep{vieillard2016transition}.
    We found that while TZs in \sigd{} and \textit{onr} cells anchored properly
    to the plasma membrane, they were unable to either establish or maintain
    membrane connections, and were rendered cytoplasmic (Figure 5A and B) similar to
    \textit{dila; cby} mutants.
    Although we were not able to determine the localization of Exo84 due to the
    lack of available reagents,
    we found that GFP-tagged Exo70 localized to centrioles (Figure 4D).
    Exo70 can directly bind to \PIP{} and mediates the recruitment of
    the exocyst complex to the plasma membrane \citep{he2007exo70}.
    Our results suggest that the exocyst may act downstream of \PIP{} to
    enhance cilium-membrane associations, and that TZ hyperelongation and loss of
    membrane-cilium association are genetically separable phenotypes.

@@

    The majority of \PIP{} at the plasma membrane is produced by PIPKIs
    \citep{balla2013phosphoinositides}
    and these seem to have a conserved role at cilia.
    In this study, we showed that mutation of the PIPKI Skittles (Sktl)
    induced hyperelongated TZs, similar to SigD expression.
    We were able rescue TZ hyperelongation by expression of full-length Sktl to
    a large degree.
    Interestingly, some cells showed cilium-autonomous suppression of lengths.
    The development of the Drosophila male germline occurs in syncytial ``cysts''
    of cells which share the same cytoplasm, and
    our results suggest that Skittles might function \textit{in situ}
    to regulate TZ maturation in these cells.
    In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
    syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy.
    The recent discovery of the role of LCCS1-associated GLE1 protein in cilium
    function \citep{jao2017role} further supports this hypothesis.
    Thus, PIPKIs might represent novel ciliopathy-associated genes
    or genetic modifiers of disease.

@@

    \section{Methods}
    \subsection{Transgenic flies}
    Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
    and 50\% humidity.
    Stocks expressing $\beta$\textit{2t}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3}),
    $\beta$\textit{2t}::YFP-Sktl (chromosome \textit{2}) and
    Exo70-GFP
    were described previously \citep{wei2008depletion, fabian2010phosphatidylinositol}.
    $\beta$\textit{2t}::mCherry-Sktl was made as in \citep{wei2008depletion},
    and a \textit{P}-element insertion on chromosome \textit{2} was used for rescue using the low-level
    expression vector \textit{tv3} \citep{wong2005pip2}.
    Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
    by T. Avidor-Reiss \citep{basiri2014migrating}.
    \textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
    Stocks expressing GFP-tagged Chibby and Mks1 were
    provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
    The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
    Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
    A. Guichet \citep{gervais2008pip5k}.
    \textit{w}\textsuperscript{1118} was used as the wild-type control.

@@

    For Taxol treatments, testes from larvae or pupae expressing
    Ana1-tdTomato; Cep290-GFP were
    dissected into Shields and Sang M3 medium (Sigma-Aldrich) supplemented
    with a predefined
    concentration of Taxol and incubated overnight in a humidified sterile
    chamber in the dark at room temperature. They were then squashed
    in PBS and imaged live.

@@

    \section{Supplemental information}
    Includes two figures. (Pending attachment)

@@

\textbf{Supplemental figures}
Cp110 localization (pending attachment).

>>>>

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
\usepackage[charter]{mathdesign}
\usepackage[numbers]{natbib}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{lineno}
\usepackage{setspace}
\usepackage{microtype}
\graphicspath{{../figures/}}
\bibliographystyle{unsrtcurrbiol}

@@

    Ciliogenesis begins with the assembly of a nascent TZ at the tips of
    the basal body \citep{reiter2012base}.
    This nascent TZ undergoes maturation, during which its structure and protein
    composition changes, allowing for the
    establishment of a compartmentalized ciliary space bounded by the ciliary membrane
    and the TZ in which axoneme assembly and signalling can occur.
    The axoneme is a microtubule-based structure that forms the core of all cilia and flagella.
    In the Drosophila male germline, nascent TZs first assemble on basal bodies
    during early G2 phase in spermatocytes \citep{riparbelli2012assembly}.
    This occurs concomitantly with the anchoring of cilia to the plasma membrane,
    rearrangment of microtubules within the TZ \citep{gottardo2013cilium},
    and establishment of a
    ciliary membrane that will persist through meiosis
    \citep{riparbelli2012assembly} (Figure 1A).
    TZ maturation has been described in
    \textit{Paramecium} \citep{aubusson2015transition}
    \textit{Caenorrhabditis elegans} \citep{serwas2017centrioles} and
    \textit{Drosophila melanogaster} \citep{gottardo2013cilium},
    and is most readily observed by an increase in TZ length
    in the Drosophila male germline.

@@

    %
    %   Results - 1
    %
    \subsection{\PIP{} is essential for transition zone maturation}
    To investigate how the reduction of cellular \PIP{} affects ciliogenesis in the
    Drosophila male germline,
    we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
    under the spermatocyte-specific $\beta$2-tubulin promoter (referred to herein as \sigd{}),
    \citep{wei2008depletion}.
    Note that \sigd{} corresponds to ``SigD-high'' in \citep{fabian2010phosphatidylinositol}.
    SigD dephosphorylates \PIP{} \textit{in vivo},
    and we previously showed that \sigd{} induces male sterility
    due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
    To examine whether these were caused by aberrant TZ function,
    we examined the localization of fluorescently-tagged
    centriolar/basal body protein
    Ana1 (homolog of CEP295) \citep{goshima2007genes, blachon2009proximal}
    and the conserved TZ protein Cep290 \citep{basiri2014migrating}
    during early steps of cilium assembly in spermatocytes in both
    wild-type controls and \sigd{}.
    As shown in Figure 1,
    while Cep290 looks similar in control and \sigd{} in early G2 phase
    when TZs are still immature, 
    it grows to significantly longer lengths in \sigd{}
    compared to wild-type controls by the end of the G2 phase following
    the period of TZ maturation in spermatocytes.
    In contrast to the \textit{cep290} mutant, which contains
    longer than normal basal bodies \citep{basiri2014migrating},
    Ana1 length was not affected in \sigd{},
    and we did not observe a strong
    correlation between Cep290 and Ana1 lengths (Figure 1C).
    We previously showed that the structure of basal bodies
    from electron microscopy was normal, and that the centriolar
    markers GFP-PACT and Sas-4 \citep{basto2006flies}
    were normal when immunostained for
    in controls and \sigd{}.
    \citep{wei2008depletion}
    TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
    Mks1 \citep{vieillard2016transition}
    showed hyperelongation in \sigd{} (Figure 1D),
    suggesting that this phenotype is not specific to Cep290 but is shared
    by other members of the Drosophila TZ.
    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%
    in spermatocytes at late G2 phase)
    and showed high intra-cyst correlation (\textgreater 0.95) suggestive
    of a dosage-based response to a shared cellular factor,
    presumably SigD.
    Despite the persistence of hyperelongated TZs through meiosis,
    axonemes were able to
    elongate normally in post-meiotic cells (Figure 1E).
    However, as we showed previously, the ultrastructure of these axonemes
    was frequently aberrant,
    either lacking symmetry completely or containing triplet microtubules
    in addition to the usual doublets \citep{wei2008depletion}.

@@

   % Since Sktl expression suppressed TZ hyperelongation,
   % we investigated whether Sktl could localize to centrioles or cilia
   % in the Drosophila germline.
    Xu \textit{et al}. showed the vertebrate PIPKI$\gamma$ to be
    important for cilium formation in cultured cell lines
    \citep{xu2014pipkigamma}.
    As shown in Figure 2D, Drosophila PIPKIs arose from the recent duplication of
    the ancestral PIPKI gene,
    and are not orthologous to specific vertebrate PIPKI isoforms.
    Sktl has diverged more than its paralog PIP5K59B, and seems
    to be functionally related to PIPKI$\gamma$ in its roles at cilia,
    as well as the \textit{C. elegans} PPK-1 (See supplementary data in \citep{xu2014pipkigamma}).
    However, unlike the human PIPKI$\gamma$, which functions to license TZ assembly
    by promoting CP110 removal from basal bodies \citep{xu2016phosphatidylinositol},
    our results suggest that Sktl functions in
    regulating TZ length in the Drosophila male germline
    but not TZ assembly.
    Neither inactivation nor overexpression of \textit{cp110} affects
    cilium formation in Drosophila, and Cp110
    and is removed from basal bodies in the earliest stages of G2 phase in the male germline
    \citep{franz2013cp110}.

@@

    %
    %   Results - 4
    %
    \subsection{The \textit{onion rings} mutant decouples defects found in cells with reduced levels of \PIP{}}
    We previously showed that male flies homozygous for the \textit{onion rings}
    (\textit{onr}) mutant of Drosophila Exo84 were sterile, and had phenotypes
    similar to \sigd{} such as defects in cell polarity \citep{wei2008depletion}.
    Exo84 is a component of the octameric exocyst complex, which binds
    \PIP{} and regulates membrane trafficking at the plasma membrane.
    To investigate whether defects in TZ hyperelongation could be explained by
    defective Exo84 function, we examined TZs in \textit{onr} mutants.
    We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 4C),
    suggesting that Exo84 is dispensable for TZ maturation.

    Due to the involvement of exocyst in membrane trafficking at the plasma membrane,
    we examined whether cilium-associated membrane dynamics were affected in \sigd{}
    or \textit{onr} mutants similar to \textit{dila; cby} mutants
    \citep{vieillard2016transition}.
    We found that while TZs in \sigd{} and \textit{onr} cells anchored properly
    to the plasma membrane, they were unable to either establish or maintain
    membrane connections, and were rendered cytoplasmic (Figure 4A and B) similar to
    \textit{dila; cby} mutants.
    Although we were not able to determine the localization of Exo84 due to the
    lack of available reagents,
    we found that GFP-tagged Exo70 localized to centrioles (Figure 4D).
    Exo70 can directly bind to \PIP{} and mediates the recruitment of
    the exocyst complex to the plasma membrane \citep{he2007exo70}.
    Our results suggest that the exocyst may act downstream of \PIP{} to
    enhance cilium-membrane associations, and that TZ hyperelongation and loss of
    membrane-cilium association are genetically separable phenotypes.

@@

    The majority of \PIP{} at the plasma membrane is produced by PIPKIs
    \citep{balla2013phosphoinositides, hammond2012pi4p}
    and these seem to have a conserved role at cilia.
    In this study, we showed that mutation of the PIPKI Skittles (Sktl)
    induced hyperelongated TZs, similar to SigD expression.
    We were able rescue TZ hyperelongation by expression of full-length Sktl to
    a large degree.
    Interestingly, some cells showed cilium-autonomous suppression of lengths.
    The development of the Drosophila male germline occurs in syncytial ``cysts''
    of cells which share the same cytoplasm, and
    our results suggest that Skittles might function \textit{in situ}
    to regulate TZ maturation in these cells.
    In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
    syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy.
    The recent discovery of the role of LCCS1-associated GLE1 protein in cilium
    function \citep{jao2017role} further supports this hypothesis.
    Thus, PIPKIs might represent novel ciliopathy-associated genes
    or genetic modifiers of disease.

@@

    \section{Methods}
    \subsection{Transgenic flies}
    Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
    and 50\% humidity.
    Stocks expressing $\beta$\textit{2t}::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3}),
    $\beta$\textit{2t}::YFP-Sktl (chromosome \textit{2}) and
    % placeholder - Exo70 is from where?
    $\beta$\textit{2t}::mCherry-Sktl was made as in \citep{wei2008depletion},
    and a \textit{P}-element insertion on chromosome \textit{2} was used for rescue using the low-level
    expression vector \textit{tv3} \citep{wong2005pip2}.
    Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
    by T. Avidor-Reiss \citep{basiri2014migrating}.
    \textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
    Stocks expressing GFP-tagged Chibby and Mks1 were
    provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
    The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
    Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
    A. Guichet \citep{gervais2008pip5k}.
    \textit{w}\textsuperscript{1118} was used as the wild-type control.

@@

    For Taxol treatments, testes from larvae or pupae expressing
    Ana1-tdTomato; Cep290-GFP were
    dissected into Shields and Sang M3 medium (Sigma-Aldrich) supplemented
    with a predefined
    concentration of Taxol (Sigma-Aldrich)
    and incubated overnight in a humidified sterile
    chamber in the dark at room temperature. They were then squashed
    in PBS and imaged live.

@@

@@
